---
title: "KLU_APC2_Jinghang_Mountz_Data_Presentation"
author: "Li Jinghang, Ellie Mountz"
date: "7/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

``` {r dataCollect, include = FALSE, echo = FALSE}
rm(list=ls())
pacman::p_load(rio)
library(tibble)
# IMPORTING Data ###########################################################
data <- import("~/Desktop/GitHub/KLU_APC2_Jinghang_Mountz_7_20_2020/Appending_to_Master/KLU_APC2_Master_2020_07_01.xlsx")
Scan_Number <- import("~/Desktop/GitHub/KLU_APC2_Jinghang_Mountz_7_20_2020/Appending_to_Master/NormalAging_DataGathering.xlsx")
activation <- import("~/Desktop/GitHub/KLU_APC2_Jinghang_Mountz_7_20_2020/Appending_to_Master/activ_values.txt")
AI <- import("~/Desktop/GitHub/KLU_APC2_Jinghang_Mountz_7_20_2020/Appending_to_Master/AI.txt")
FWHM <- import("~/Desktop/GitHub/KLU_APC2_Jinghang_Mountz_7_20_2020/Appending_to_Master/FWHM.txt")
FWHM <- abs(FWHM)
# Filter Data ##############################################################
data <- data[-c(which(data$FaceNames_Exclude == 'Yes')),] #Exclude for scanning issues

list <- match(Scan_Number$ScanID,data$Vault_Scan_ID) #Only include 1 scan/subject
index <- which(list!=0,arr.ind = T)
list <- na.omit(match(Scan_Number$ScanID, data$Vault_Scan_ID))
data$Scan_Number <- NA
data$Scan_Number[list] <- Scan_Number$`Scan Number`[index]
data <- data[c(which(data$Scan_Number == 1)),]

list <- match(activation$Scan_ID,data$Vault_Scan_ID) #Match up all calculated valuese with correct scan
index <- which(list!=0,arr.ind = T)
list <- na.omit(match(activation$Scan_ID, data$Vault_Scan_ID))

#creating new variables that are going to be appended
data$Subject_ID <- NA
data$Scan_ID <- NA
data$Left_Hippocampus_Activation <- NA
data$Right_Hippocampus_Activation <- NA
data$Left_DLPFC_Activation <- NA
data$Right_DLPFC_Activation <- NA
data$Hippocampus_AI <- NA
data$DLPFC_AI <-NA
data$Left_Hippocampus_FWHM <- NA
data$Right_Hippocampus_FWHM <- NA
data$Left_DLPFC_FWHM <- NA
data$Right_DLPFC_FWHM <- NA

#appending
data$Subject_ID[list] <- activation$Subject_ID[index]
data$Scan_ID[list] <- activation$Scan_ID[index]
data$Left_Hippocampus_Activation[list] <- activation[,3][index]
data$Right_Hippocampus_Activation[list] <- activation[,4][index]
data$Left_DLPFC_Activation[list] <- activation[,5][index]
data$Right_DLPFC_Activation[list] <- activation[,6][index]
data$Hippocampus_AI[list] <- AI[,3][index]
data$DLPFC_AI[list] <- AI[,4][index]

data$Left_Hippocampus_FWHM[list] <- FWHM[,3]
data$Right_Hippocampus_FWHM[list] <- FWHM[,4]
data$Left_DLPFC_FWHM[list] <- FWHM[,5]
data$Right_DLPFC_FWHM[list] <- FWHM[,6]
# Recode Variables ##############################################################
data$Race_cat <- data$Race != 'White' #not white = 1 (True)
data$Education_cat <- data$Education > 12  #higher education = 1 (True)
data$Sex_cat <- (data$Sex == 'Male') #1 = male
data$Sex_cat[data$Sex == "NaN"] = NA
data$LETTER_FLUENCY <- (data$FLUENA + data$FLUENF+ data$FLUENS) / 3
data$STRINTERFERENCE <- (data$STRCW - data$STRCOL) / data$STRCOL
data$PiB_STATUS_CODE <- (data$PiBStatus_SUVR_GTM_FS_Global == "pos")
data$PiB_STATUS_CODE[data$PiBStatus_SUVR_GTM_FS_Global == "NaN"] = NA
data$APOE_CODE[data$APOE_CODE == "NaN"] = NA
data$Abs_Hippocampus_AI <- abs(data$Hippocampus_AI)
data$Abs_DLPFC_AI <- abs(data$DLPFC_AI)
data$FaceName_PostScanAccuracy[data$FaceName_PostScanAccuracy == "NA"] <- NA
data$FaceName_PostScanAccuracy <- as.numeric(data$FaceName_PostScanAccuracy)

# Cognitive Data Normalization ##################################################
#Memory
REYIM_Mean <- 15.4 #doi: 10.1136/jnnp.2004.045567
REYDE_Mean <- 14.7 #doi: 10.1136/jnnp.2004.045567
#Visiospatial
REYCO_Mean <-22.3 #doi: 10.1136/jnnp.2004.045567
BLOCKDES_Mean <- 11.4 #doi: 10.1136/jnnp.2004.045567
#Language
BOSTON1_Mean <- 26.9 #doi: 10.1136/jnnp.2004.045567
FLUEN_Mean <- 15.6 #doi: 10.1136/jnnp.2004.045567
#Executive/Attention
TRAILAS_Mean <- 45.6 #doi: 10.1136/jnnp.2004.045567
TRAILBS_Mean <-107.5 #doi: 10.1136/jnnp.2004.045567
SPANSF_Mean <- 6.4 #doi: 10.1136/jnnp.2004.045567
SPANSB_Mean <- 4.4 #doi: 10.1136/jnnp.2004.045567
DIGSYMWR_Mean <- 46.8 #doi: 10.1136/jnnp.2004.045567

#Citation Notes: - add n values
#Our sample: avg age: 74.8; >12 yrs education: 72%, avg. education: 14.897

#doi: 10.1136/jnnp.2004.045567 - avg. age (for normal subjects): 79.5; >12 yrs education: 61.5%
#Most means from this source are more low/poor compared to our sample

# Z Transform ####################################################################
#Negative z value means that lower value = higher performance
# doi:10.1016/j.jalz.2017.12.003 - method of composite calculation
#doi/ 10.1136/jnnp.2004.045567 - standard deviations from normative data
REYIM_Z <- (data$REYIM-REYIM_Mean) / 4.8
REYDE_Z <- (data$REYDE-REYDE_Mean) / 4.8
REYCO_Z <- (data$REYCO-REYCO_Mean) / 2.1
BLOCKDES_Z <- (data$BLOCKDES-BLOCKDES_Mean) / 4.8
BOSTON1_Z <-(data$BOSTON1-BOSTON1_Mean) / 2.6
FLUEN_Z <- (data$FLUEN-FLUEN_Mean) / 4.8
TRAILAS_Z <- (data$TRAILAS-TRAILAS_Mean) / 17.5
TRAILAS_Z_INV <- -1*TRAILAS_Z
SPANSF_Z <- (data$SPANSF-SPANSF_Mean) / 1.2
SPANSB_Z <- (data$SPANSB-SPANSB_Mean) / 1.2
TRAILBS_Z <- (data$TRAILBS-TRAILBS_Mean) / 49.3
TRAILBS_Z_INV <- -1*TRAILBS_Z
DIGSYMWR_Z <- (data$DIGSYMWR-DIGSYMWR_Mean) / 12.3

# Domain Scores #########################################################################
#doi:10.1016/j.jalz.2017.12.003., doi:10.1080/13607860903071014. (Both Beth Snitz articles), https://www.ncbi.nlm.nih.gov/books/NBK285344/ - for SPANSB in Executive
data$memory <- (REYIM_Z + REYDE_Z) /2
data$visiospatial <- (REYCO_Z + BLOCKDES_Z)/2
data$language <- (BOSTON1_Z +FLUEN_Z) / 2
data$executive <- (TRAILBS_Z_INV +SPANSB_Z) / 2
data$attention <- (TRAILAS_Z_INV + SPANSF_Z) / 2
data$executive_attention <- (TRAILAS_Z_INV + TRAILBS_Z_INV + SPANSF_Z + SPANSB_Z + DIGSYMWR_Z) / 5

#Citation Notes: - add n values
#Our sample: avg age: 74.8; >12 yrs education: 72%, avg. education: 14.897

#doi: 10.1136/jnnp.2004.045567 - avg. age (for normal subjects): 79.5; >12 yrs education: 61.5%
#Most means from this source are more low/poor compared to our sample

# Z Transform ####################################################################
#Negative z value means that lower value = higher performance
# doi:10.1016/j.jalz.2017.12.003 - method of composite calculation
#doi/ 10.1136/jnnp.2004.045567 - standard deviations from normative data
REYIM_Z <- (data$REYIM-REYIM_Mean) / 4.8
REYDE_Z <- (data$REYDE-REYDE_Mean) / 4.8
REYCO_Z <- (data$REYCO-REYCO_Mean) / 2.1
BLOCKDES_Z <- (data$BLOCKDES-BLOCKDES_Mean) / 4.8
BOSTON1_Z <-(data$BOSTON1-BOSTON1_Mean) / 2.6
FLUEN_Z <- (data$FLUEN-FLUEN_Mean) / 4.8
TRAILAS_Z <- (data$TRAILAS-TRAILAS_Mean) / 17.5
TRAILAS_Z_INV <- -1*TRAILAS_Z
SPANSF_Z <- (data$SPANSF-SPANSF_Mean) / 1.2
SPANSB_Z <- (data$SPANSB-SPANSB_Mean) / 1.2
TRAILBS_Z <- (data$TRAILBS-TRAILBS_Mean) / 49.3
TRAILBS_Z_INV <- -1*TRAILBS_Z
DIGSYMWR_Z <- (data$DIGSYMWR-DIGSYMWR_Mean) / 12.3

# Domain Scores #########################################################################
#doi:10.1016/j.jalz.2017.12.003., doi:10.1080/13607860903071014. (Both Beth Snitz articles), https://www.ncbi.nlm.nih.gov/books/NBK285344/ - for SPANSB in Executive
data$memory <- (REYIM_Z + REYDE_Z) /2
data$visiospatial <- (REYCO_Z + BLOCKDES_Z)/2
data$language <- (BOSTON1_Z +FLUEN_Z) / 2
data$executive <- (TRAILBS_Z_INV +SPANSB_Z) / 2
data$attention <- (TRAILAS_Z_INV + SPANSF_Z) / 2
data$executive_attention <- (TRAILAS_Z_INV + TRAILBS_Z_INV + SPANSF_Z + SPANSB_Z + DIGSYMWR_Z) / 5
```

``` {r intraclass_correlation, include = FALSE, echo = FALSE}
#Intraclass Correlation ################################################################
# Pearson (Linear Correlation between composite and raw scores)
library("irr")
#Memory
REYIM_Pearson_Correlation <- cor(data$memory, data$REYIM, use = "complete.obs")
REYDE_Pearson_Correlation <- cor(data$memory, data$REYDE, use = "complete.obs")

# Visiospatial
BLOCKDES_Pearson_Correlation <- cor(data$visiospatial, data$BLOCKDES, use = "complete.obs")
REYCO_Pearson_Correlation <- cor(data$visiospatial, data$REYCO, use = "complete.obs")

#Langugae
BOSTON1_Pearson_Correlation <- cor(data$language, data$BOSTON1, use = "complete.obs")
FLUEN_Pearson_Correlation <- cor(data$language, data$FLUEN, use = "complete.obs")

#Executive
TRAILBS_Pearson_Correlation <- cor(data$executive, -1*data$TRAILBS, use = "complete.obs")
SPANSB_Pearson_Correlation <- cor(data$executive, data$SPANSB, use = "complete.obs")

#Attention
TRAILAS_Pearson_Correlation <- cor(data$attention, -1*data$TRAILAS, use = "complete.obs")
SPANSF_Pearson_Correlation <- cor(data$attention, data$SPANSF, use = "complete.obs")

#Executive_Attention
TRAILBS_Combo_Pearson_Correlation <- cor(data$executive_attention, -1*data$TRAILBS, use = "complete.obs")
TRAILAS_Combo_Pearson_Correlation <- cor(data$executive_attention, -1*data$TRAILAS, use = "complete.obs")
SPANSF_Combo_Pearson_Correlation <- cor(data$executive_attention, data$SPANSF, use = "complete.obs")
DIGSYMWR_Combo_Pearson_Correlation <- cor(data$executive_attention, data$DIGSYMWR, use = "complete.obs")
SPANSB_Combo_Pearson_Correlation <- cor(data$executive_attention, data$SPANSB, use = "complete.obs")
```

``` {r pval_calc, echo = FALSE, include = FALSE}
#For p-values
lmp <- function (modelobject) {
  if (class(modelobject) != "lm") stop("Not an object of class 'lm' ")
  f <- summary(modelobject)$fstatistic
  p <- pf(f[1],f[2],f[3],lower.tail=F)
  attributes(p) <- NULL
  return(p)
}
```

``` {r raw_hippocampus, echo = FALSE}
# Regressions ##############################################################################################################################

mdl_hippocampus_AI <- lm(Hippocampus_AI ~ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_CODE, data = data)

raw_hippocampus_rsquared <- summary(mdl_hippocampus_AI)$r.squared
raw_hippocampus_fstat <- summary(mdl_hippocampus_AI)$fstatistic[1]
raw_hippocampus_df1 <- summary(mdl_hippocampus_AI)$fstatistic[2]
raw_hippocampus_df2 <- summary(mdl_hippocampus_AI)$fstatistic[3]
raw_hippocampus_pval <- lmp(mdl_hippocampus_AI)
```

``` {r raw_DLPFC, echo = FALSE}
mdl_DLPFC_AI <- lm(DLPFC_AI ~  Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_CODE, data = data)

raw_DLPFC_rsquared <- summary(mdl_DLPFC_AI)$r.squared
raw_DLPFC_fstat <- summary(mdl_DLPFC_AI)$fstatistic[1]
raw_DLPFC_df1 <- summary(mdl_DLPFC_AI)$fstatistic[2]
raw_DLPFC_df2 <- summary(mdl_DLPFC_AI)$fstatistic[3]
raw_DLPFC_pval <- lmp(mdl_DLPFC_AI)
```

``` {r Abs_hippocampus, echo = FALSE}
mdl_Abs_hippocampus_AI <- lm(Abs_Hippocampus_AI ~ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_CODE, data = data)

abs_hippocampus_rsquared <- summary(mdl_Abs_hippocampus_AI)$r.squared
abs_hippocampus_fstat <- summary(mdl_Abs_hippocampus_AI)$fstatistic[1]
abs_hippocampus_df1 <- summary(mdl_Abs_hippocampus_AI)$fstatistic[2]
abs_hippocampus_df2 <- summary(mdl_Abs_hippocampus_AI)$fstatistic[3]
abs_hippocampus_pval <- lmp(mdl_Abs_hippocampus_AI)
```

``` {r Abs_DLPFC, echo = FALSE}
mdl_Abs_DLPFC_AI <- lm(Abs_DLPFC_AI ~ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_CODE, data = data)

abs_DLPFC_rsquared <- summary(mdl_Abs_DLPFC_AI)$r.squared
abs_DLPFC_fstat <- summary(mdl_Abs_DLPFC_AI)$fstatistic[1]
abs_DLPFC_df1 <- summary(mdl_Abs_DLPFC_AI)$fstatistic[2]
abs_DLPFC_df2 <- summary(mdl_Abs_DLPFC_AI)$fstatistic[3]
abs_DLPFC_pval <- lmp(mdl_Abs_DLPFC_AI)

```

``` {r memory_raw, echo = FALSE }
# # Cognitive Factors - Raw AI ################################################################
#executive1 (0.0299), executive_attention (0.02)

mdl_memory_raw_AI <- lm(memory ~ FaceName_PostScanAccuracy+DLPFC_AI + Hippocampus_AI+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_CODE, data = data)

memory_raw_rsquared <- summary(mdl_memory_raw_AI)$r.squared
memory_raw_fstat <- summary(mdl_memory_raw_AI)$fstatistic[1]
memory_raw_df1 <- summary(mdl_memory_raw_AI)$fstatistic[2]
memory_raw_df2 <- summary(mdl_memory_raw_AI)$fstatistic[3]
memory_raw_pval <- lmp(mdl_memory_raw_AI)
```

``` {r visiospatial_raw, echo = FALSE}
mdl_visiospatial_raw_AI <- lm(visiospatial ~ FaceName_PostScanAccuracy+DLPFC_AI + Hippocampus_AI+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_CODE, data = data)

visiospatial_raw_rsquared <- summary(mdl_visiospatial_raw_AI)$r.squared
visiospatial_raw_fstat <- summary(mdl_visiospatial_raw_AI)$fstatistic[1]
visiospatial_raw_df1 <- summary(mdl_visiospatial_raw_AI)$fstatistic[2]
visiospatial_raw_df2 <- summary(mdl_visiospatial_raw_AI)$fstatistic[3]
visiospatial_raw_pval <- lmp(mdl_visiospatial_raw_AI)
```

``` {r language_raw, echo = FALSE}
mdl_language_raw_AI <- lm(language ~ FaceName_PostScanAccuracy+DLPFC_AI + Hippocampus_AI+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_CODE, data = data)

language_raw_rsquared <- summary(mdl_language_raw_AI)$r.squared
language_raw_fstat <- summary(mdl_language_raw_AI)$fstatistic[1]
language_raw_df1 <- summary(mdl_language_raw_AI)$fstatistic[2]
language_raw_df2 <- summary(mdl_language_raw_AI)$fstatistic[3]
language_raw_pval <- lmp(mdl_language_raw_AI)
```

``` {r executive_raw, echo = FALSE}
mdl_executive_raw_AI <- lm(executive ~ FaceName_PostScanAccuracy+DLPFC_AI + Hippocampus_AI+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_CODE, data = data)

executive_raw_rsquared <- summary(mdl_executive_raw_AI)$r.squared
executive_raw_fstat <- summary(mdl_executive_raw_AI)$fstatistic[1]
executive_raw_df1 <- summary(mdl_executive_raw_AI)$fstatistic[2]
executive_raw_df2 <- summary(mdl_executive_raw_AI)$fstatistic[3]
executive_raw_pval <- lmp(mdl_executive_raw_AI)
```

``` {r attention_raw, echo = FALSE}
mdl_attention_raw_AI <- lm(attention ~ FaceName_PostScanAccuracy+DLPFC_AI + Hippocampus_AI+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_CODE, data = data)

attention_raw_rsquared <- summary(mdl_attention_raw_AI)$r.squared
attention_raw_fstat <- summary(mdl_attention_raw_AI)$fstatistic[1]
attention_raw_df1 <- summary(mdl_attention_raw_AI)$fstatistic[2]
attention_raw_df2 <- summary(mdl_attention_raw_AI)$fstatistic[3]
attention_raw_pval <- lmp(mdl_attention_raw_AI)
```

``` {r executive_attention_raw, echo = FALSE}
mdl_executive_attention_raw_AI <- lm(executive_attention ~ FaceName_PostScanAccuracy+DLPFC_AI + Hippocampus_AI+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_CODE, data = data)

executive_attention_raw_rsquared <- summary(mdl_executive_attention_raw_AI)$r.squared
executive_attention_raw_fstat <- summary(mdl_executive_attention_raw_AI)$fstatistic[1]
executive_attention_raw_df1 <- summary(mdl_executive_attention_raw_AI)$fstatistic[2]
executive_attention_raw_df2 <- summary(mdl_executive_attention_raw_AI)$fstatistic[3]
executive_attention_raw_pval <- lmp(mdl_executive_attention_raw_AI)
```

``` {r memory_abs, echo = FALSE}
# Cognitive Factors  - Absolute AI################################################################
#Language (0.06), executive1 (0.0299), executive_attention (0.02)
mdl_memory_abs_AI <- lm(memory ~ FaceName_PostScanAccuracy+Abs_DLPFC_AI + Abs_Hippocampus_AI+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_CODE, data = data)

memory_abs_rsquared <- summary(mdl_memory_abs_AI)$r.squared
memory_abs_fstat <- summary(mdl_memory_abs_AI)$fstatistic[1]
memory_abs_df1 <- summary(mdl_memory_abs_AI)$fstatistic[2]
memory_abs_df2 <- summary(mdl_memory_abs_AI)$fstatistic[3]
memory_abs_pval <- lmp(mdl_memory_abs_AI)

```

``` {r visiospatial_abs, echo = FALSE}

mdl_visiospatial_abs_AI <- lm(visiospatial ~ FaceName_PostScanAccuracy+Abs_DLPFC_AI + Abs_Hippocampus_AI+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_CODE, data = data)

visiospatial_abs_rsquared <- summary(mdl_visiospatial_abs_AI)$r.squared
visiospatial_abs_fstat <- summary(mdl_visiospatial_abs_AI)$fstatistic[1]
visiospatial_abs_df1 <- summary(mdl_visiospatial_abs_AI)$fstatistic[2]
visiospatial_abs_df2 <- summary(mdl_visiospatial_abs_AI)$fstatistic[3]
visiospatial_abs_pval <- lmp(mdl_visiospatial_abs_AI)

```

``` {r language_abs, echo = FALSE}

mdl_language_abs_AI <- lm(language ~ FaceName_PostScanAccuracy+Abs_DLPFC_AI + Abs_Hippocampus_AI+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_CODE, data = data)

language_abs_rsquared <- summary(mdl_language_abs_AI)$r.squared
language_abs_fstat <- summary(mdl_language_abs_AI)$fstatistic[1]
language_abs_df1 <- summary(mdl_language_abs_AI)$fstatistic[2]
language_abs_df2 <- summary(mdl_language_abs_AI)$fstatistic[3]
language_abs_pval <- lmp(mdl_language_abs_AI)

```

``` {r executive_abs, echo = FALSE}
mdl_executive_abs_AI <- lm(executive ~ FaceName_PostScanAccuracy+Abs_DLPFC_AI + Abs_Hippocampus_AI+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_CODE, data = data)

executive_abs_rsquared <- summary(mdl_executive_abs_AI)$r.squared
executive_abs_fstat <- summary(mdl_executive_abs_AI)$fstatistic[1]
executive_abs_df1 <- summary(mdl_executive_abs_AI)$fstatistic[2]
executive_abs_df2 <- summary(mdl_executive_abs_AI)$fstatistic[3]
executive_abs_pval <- lmp(mdl_executive_abs_AI)
```

``` {r attention_abs, echo = FALSE}
mdl_attention_abs_AI <- lm(attention ~ FaceName_PostScanAccuracy+Abs_DLPFC_AI + Abs_Hippocampus_AI+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_CODE, data = data)

attention_abs_rsquared <- summary(mdl_attention_abs_AI)$r.squared
attention_abs_fstat <- summary(mdl_attention_abs_AI)$fstatistic[1]
attention_abs_df1 <- summary(mdl_attention_abs_AI)$fstatistic[2]
attention_abs_df2 <- summary(mdl_attention_abs_AI)$fstatistic[3]
attention_abs_pval <- lmp(mdl_attention_abs_AI)
```

``` {r executive_attention_abs, echo = FALSE}
mdl_executive_attention_abs_AI <- lm(executive_attention ~ FaceName_PostScanAccuracy+Abs_DLPFC_AI + Abs_Hippocampus_AI+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_CODE, data = data)

executive_attention_abs_rsquared <- summary(mdl_executive_attention_abs_AI)$r.squared
executive_attention_abs_fstat <- summary(mdl_executive_attention_abs_AI)$fstatistic[1]
executive_attention_abs_df1 <- summary(mdl_executive_attention_abs_AI)$fstatistic[2]
executive_attention_abs_df2 <- summary(mdl_executive_attention_abs_AI)$fstatistic[3]
executive_attention_abs_pval <- lmp(mdl_executive_attention_abs_AI)
```

``` { r new_model, echo = FALSE}

```

``` {r modelSetUp, echo = FALSE, include = FALSE}
if (!require("sjPlot")) install.packages("sjPlot")
library(sjPlot)
if (!require("kableExtra")) install.packages("kableExtra")
library(knitr)
library(kableExtra)
if (!require("scales")) install.packages("scales")
library(scales)
```

## Cohort Demographics:

``` {r demographicsData, echo = FALSE}
# Demographics Table ###############################################################

#Calculate Data - Some data missing
num_subjects <- nrow(data)

n_education <- length(data$Education_cat[!is.na(data$Education_cat)])
mean_education <- mean(data$Education, na.rm = TRUE)
stdv_education <- sd(data$Education, na.rm = TRUE)
education_over_12 <- sum(data$Education_cat, na.rm = TRUE)
education_under_12 <- length(data$Education_cat)-sum(data$Education_cat, na.rm = TRUE) - sum(is.na(data$Education_cat))
percent_over_12 <- education_over_12 / (length(data$Education_cat) - sum(is.na(data$Education_cat)))
percent_under_12 <- education_under_12 / (length(data$Education_cat) - sum(is.na(data$Education_cat)))

n_age <- length(data$Age_CurrentVisit[!is.na(data$Age_CurrentVisit)])
mean_age <- mean(data$Age_CurrentVisit, na.rm = TRUE)
age_stdv <- sd(data$Age_CurrentVisit, na.rm = TRUE)

n_sex <- length(data$Sex_cat[!is.na(data$Sex_cat)])
male_count <- sum(data$Sex == "Male", na.rm = TRUE)
percent_male <- male_count / (length(data$Sex) - sum(data$Sex == ""))
female_count <- sum(data$Sex == "Female", na.rm = TRUE)
percent_female <- female_count / (length(data$Sex) - sum(data$Sex == ""))

n_race <- length(data$Race_cat[!is.na(data$Race_cat)])
white_count <- sum(data$Race == "White")
percent_white <- white_count / (length(data$Race) - sum(data$Race == ""))
black_count <- sum(data$Race == "Black")
percent_black <- black_count / (length(data$Race) - sum(data$Race == ""))
asian_count <- sum(data$Race == "Asian")
percent_asian <- asian_count / (length(data$Race) - sum(data$Race == ""))

```

<div style="margin-bottom:100px;">
``` {r, echo = FALSE}
#Make Table
demographic_data <- data.frame(Variable = c("Total_Subjects","n", "Mean", "Standard Deviation", "Over 12 Years", "Under 12 Years", "n","Mean", "Standard Deviation", "n","Male Count", "Female Count", "n","White Count", "Black Count", "Asian Count"),
                               Value = c(num_subjects, n_education, mean_education, stdv_education, education_over_12, education_under_12,n_age, mean_age, age_stdv, n_sex, male_count, female_count, n_race, white_count,black_count,asian_count),
                               Percent = c("", "", "","", label_percent()(percent_over_12), label_percent()(percent_under_12),"","","","",label_percent()(percent_male), label_percent()(percent_female),"",label_percent()(percent_white),label_percent()(percent_black),label_percent()(percent_asian)))

kable(demographic_data, caption = "Demographic data for normal aging", digits = 2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                pack_rows("Education", 2,6) %>%
                pack_rows("Age", 7,9) %>%
                pack_rows("Sex", 10,12) %>%
                pack_rows("Race", 13,16)

```
</div>

## Regression Models:

## Hemispheric Asymmetry Models
**Hippocampus Raw Asymmetry Index Data**
<div style="margin-bottom:100px;">
``` {r raw_hippocampus_data, echo = FALSE}
raw_hippocampus_data <- data.frame(Variable = c(paste("F( ", raw_hippocampus_df1, ",", raw_hippocampus_df2,")"),"R^2","p-value"),
                               Value = c(raw_hippocampus_fstat,raw_hippocampus_rsquared,raw_hippocampus_pval))

kable(raw_hippocampus_data, caption = "Hippocampus Raw AI Model Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r raw_hippocampus_coefficients, echo = FALSE}

tab_model(mdl_hippocampus_AI, dv.labels = "Hippocampus Raw AI",
          pred.labels = c("Intercept","Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**DLPFC Raw Asymmetry Index Data** 
<div style="margin-bottom:100px;">
``` {r raw_DLPFC_data, echo = FALSE}
raw_DLPFC_data <- data.frame(Variable = c(paste("F( ", raw_DLPFC_df1, ",", raw_DLPFC_df2,")"),"R^2","p-value"),
                               Value = c(raw_DLPFC_fstat,raw_DLPFC_rsquared,raw_DLPFC_pval))

kable(raw_DLPFC_data, caption = "DLPFC Raw AI Model Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r raw_DLPFC_coefficients, echo = FALSE}

tab_model(mdl_DLPFC_AI, dv.labels = "DLPFC Raw AI",
          pred.labels = c("Intercept","Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>


**Hippocampus Absolute Asymmetry Index Data**
<div style="margin-bottom:100px;">
``` {r abs_hippocampus_data, echo = FALSE}
abs_hippocampus_data <- data.frame(Variable = c(paste("F( ", abs_hippocampus_df1, ",", abs_hippocampus_df2,")"),"R^2","p-value"),
                               Value = c(abs_hippocampus_fstat,abs_hippocampus_rsquared,abs_hippocampus_pval))

kable(abs_hippocampus_data, caption = "Hippocampus Absolute AI Model Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

``` {r abs_hippocampus_coefficients, echo = FALSE}
tab_model(mdl_Abs_hippocampus_AI, dv.labels = "Hippocampus Absolute AI",
          pred.labels = c("Intercept","Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**DLPFC Absolute Asymmetry Index Data** 
<div style="margin-bottom:100px;">
``` {r abs_DLPFC_data, echo = FALSE}
abs_DLPFC_data <- data.frame(Variable = c(paste("F( ", abs_DLPFC_df1, ",", abs_DLPFC_df2,")"),"R^2","p-value"),
                               Value = c(abs_DLPFC_fstat,abs_DLPFC_rsquared,abs_DLPFC_pval))

kable(abs_DLPFC_data, caption = "DLPFC Absolute AI Model Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r abs_DLPFC_coefficients, echo = FALSE}
tab_model(mdl_Abs_DLPFC_AI, dv.labels = "DLPFC Absolute AI",
          pred.labels = c("Intercept","Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

## Cogntivie Domains

**Interclass Correlation**

``` {r domain_correlation, echo = FALSE}
# Correlation Tables ########################################################################
Pearson_Correlation_data <- data.frame(Variable = c("Modified Rey Figure Delayed Recall","Modified Rey Figure Immediate Recall", "Modified Block Design","Modified Rey Figure Copy","Boston Naming Test (30-item)","Fluency - Animals","Trails B","Digit Span Backward","Trails A","Digit Span Forward","Digit Symbol Substitution Test","Trails A","Digit Span Forward","Trails B","Digit Span Backward"),
                                       Pearson_Correlation = c(REYDE_Pearson_Correlation,REYIM_Pearson_Correlation,BLOCKDES_Pearson_Correlation,REYCO_Pearson_Correlation, BOSTON1_Pearson_Correlation, FLUEN_Pearson_Correlation, TRAILBS_Pearson_Correlation,SPANSB_Pearson_Correlation, TRAILAS_Pearson_Correlation,SPANSF_Pearson_Correlation, DIGSYMWR_Combo_Pearson_Correlation, TRAILAS_Combo_Pearson_Correlation,SPANSF_Combo_Pearson_Correlation,TRAILBS_Combo_Pearson_Correlation,SPANSB_Combo_Pearson_Correlation))
```

<div style="margin-bottom:100px;">
``` {r domain_correlation_make_table, echo=FALSE}
kable(Pearson_Correlation_data, caption = "Pearson Interclass Correlation Values for Cognitive Domains. Measures linear correlation between raw cognitive test scores and the corresponding composite cognitive domain score.", digits = 2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
  pack_rows("Memory Domain",1,2) %>%
  pack_rows("Visiospatial Domain",3,4) %>%
  pack_rows("Language Domain",5,6) %>%
  pack_rows("Executive Domain",7,8) %>%
  pack_rows("Attention Domain",9,10) %>%
  pack_rows("Executive_Attention Domain",11,15)
```
</div>

### Raw Asymmetry Index Regressions

**Memory Domain**
<div style="margin-bottom:100px;">
``` {r memory_raw_data, echo = FALSE}
memory_raw_data <- data.frame(Variable = c(paste("F( ", memory_raw_df1, ",", memory_raw_df2,")"),"R^2","p-value"),
                               Value = c(memory_raw_fstat,memory_raw_rsquared,memory_raw_pval))

kable(memory_raw_data, caption = "Memory Raw AI Model Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r memory_raw_coefficients, echo = FALSE}
tab_model(mdl_memory_raw_AI, dv.labels = "Memory - Raw AI",
          pred.labels = c("Intercept","Task Accuracy","DLPFC Raw AI", "Hippocampus Raw AI", "Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Visiospatial Domain**
<div style="margin-bottom:100px;">
``` {r visiospatial_raw_data, echo = FALSE}
visiospatial_raw_data <- data.frame(Variable = c(paste("F( ", visiospatial_raw_df1, ",", visiospatial_raw_df2,")"),"R^2","p-value"),
                               Value = c(visiospatial_raw_fstat,visiospatial_raw_rsquared,visiospatial_raw_pval))

kable(visiospatial_raw_data, caption = "Visiospatial Raw AI Model Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r visiospatial_raw_coefficients, echo = FALSE}
tab_model(mdl_visiospatial_raw_AI, dv.labels = "Visiospatial - Raw AI",
          pred.labels = c("Intercept","Task Accuracy","DLPFC Raw AI", "Hippocampus Raw AI", "Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Language Domain**
<div style="margin-bottom:100px;">
``` {r language_raw_data, echo = FALSE}
language_raw_data <- data.frame(Variable = c(paste("F( ", language_raw_df1, ",", language_raw_df2,")"),"R^2","p-value"),
                               Value = c(language_raw_fstat,language_raw_rsquared, language_raw_pval))

kable(language_raw_data, caption = "Language Raw AI Model Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r language_raw_coefficients, echo = FALSE}
tab_model(mdl_language_raw_AI, dv.labels = "Language - Raw AI",
          pred.labels = c("Intercept","Task Accuracy","DLPFC Raw AI", "Hippocampus Raw AI", "Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Executive Domain**
<div style="margin-bottom:100px;">
``` {r executive_raw_data, echo = FALSE}
executive_raw_data <- data.frame(Variable = c(paste("F( ", executive_raw_df1, ",", executive_raw_df2,")"),"R^2","p-value"),
                               Value = c(executive_raw_fstat,executive_raw_rsquared, executive_raw_pval))

kable(executive_raw_data, caption = "Executive Raw AI Model Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r executive_raw_coefficients, echo = FALSE}
tab_model(mdl_executive_raw_AI, dv.labels = "Executive - Raw AI",
          pred.labels = c("Intercept","Task Accuracy","DLPFC Raw AI", "Hippocampus Raw AI", "Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Attention Domain**
<div style="margin-bottom:100px;">
``` {r attention_raw_data, echo = FALSE}
attention_raw_data <- data.frame(Variable = c(paste("F( ", attention_raw_df1, ",", attention_raw_df2,")"),"R^2","p-value"),
                               Value = c(attention_raw_fstat,attention_raw_rsquared, attention_raw_pval))

kable(attention_raw_data, caption = "Executive Raw AI Model Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r attention_raw_coefficients, echo = FALSE}
tab_model(mdl_attention_raw_AI, dv.labels = "Attention - Raw AI",
          pred.labels = c("Intercept","Task Accuracy","DLPFC Raw AI", "Hippocampus Raw AI", "Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Executive_Attention Domain**
<div style="margin-bottom:100px;">
``` {r executive_attention_raw_data, echo = FALSE}
executive_attention_raw_data <- data.frame(Variable = c(paste("F( ", executive_attention_raw_df1, ",", executive_attention_raw_df2,")"),"R^2","p-value"),
                               Value = c(executive_attention_raw_fstat,executive_attention_raw_rsquared, executive_attention_raw_pval))

kable(executive_attention_raw_data, caption = "Executive_Attention Raw AI Model Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r executive_attention_raw_coefficients, echo = FALSE}
tab_model(mdl_executive_attention_raw_AI, dv.labels = "Executive_Attention - Raw AI",
          pred.labels = c("Intercept","Task Accuracy","DLPFC Raw AI", "Hippocampus Raw AI", "Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

### Absolute Asymmetry Index Regressions

**Memory Domain**
<div style="margin-bottom:100px;">
``` {r memory_abs_data, echo = FALSE}
memory_abs_data <- data.frame(Variable = c(paste("F( ", memory_abs_df1, ",", memory_abs_df2,")"),"R^2","p-value"),
                               Value = c(memory_abs_fstat,memory_abs_rsquared,memory_abs_pval))

kable(memory_abs_data, caption = "Memory Absolute AI Model Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r memory_abs_coefficients, echo = FALSE}
tab_model(mdl_memory_abs_AI, dv.labels = "Memory - Absolute AI",
          pred.labels = c("Intercept","Task Accuracy","DLPFC Absolute AI", "Hippocampus Absolute AI", "Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Visiospatial Domain**
<div style="margin-bottom:100px;">
``` {r visiospatial_abs_data, echo = FALSE}
visiospatial_abs_data <- data.frame(Variable = c(paste("F( ", visiospatial_abs_df1, ",", visiospatial_abs_df2,")"),"R^2","p-value"),
                               Value = c(visiospatial_abs_fstat,visiospatial_abs_rsquared,visiospatial_abs_pval))

kable(visiospatial_abs_data, caption = "Visiospatial Absolute AI Model Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r visiospatial_abs_coefficients, echo = FALSE}
tab_model(mdl_visiospatial_abs_AI, dv.labels = "Visiospatial - Absolute AI",
          pred.labels = c("Intercept","Task Accuracy","DLPFC Absolute AI", "Hippocampus Absolute AI", "Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Language Domain**
<div style="margin-bottom:100px;">
``` {r language_abs_data, echo = FALSE}
language_abs_data <- data.frame(Variable = c(paste("F( ", language_abs_df1, ",", language_abs_df2,")"),"R^2","p-value"),
                               Value = c(language_abs_fstat,language_abs_rsquared, language_abs_pval))

kable(language_abs_data, caption = "Language Absolute AI Model Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r language_abs_coefficients, echo = FALSE}
tab_model(mdl_language_abs_AI, dv.labels = "Language - Absolute AI",
          pred.labels = c("Intercept","Task Accuracy","DLPFC Absolute AI", "Hippocampus Absolute AI", "Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Executive Domain**
<div style="margin-bottom:100px;">
``` {r executive_abs_data, echo = FALSE}
executive_abs_data <- data.frame(Variable = c(paste("F( ", executive_abs_df1, ",", executive_abs_df2,")"),"R^2","p-value"),
                               Value = c(executive_abs_fstat,executive_abs_rsquared, executive_abs_pval))

kable(executive_abs_data, caption = "Executive Absolute AI Model Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r executive_abs_coefficients, echo = FALSE}
tab_model(mdl_executive_abs_AI, dv.labels = "Executive - Absolute AI",
          pred.labels = c("Intercept","Task Accuracy","DLPFC Absolute AI", "Hippocampus Absolute AI", "Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Attention Domain**
<div style="margin-bottom:100px;">
``` {r attention_abs_data, echo = FALSE}
attention_abs_data <- data.frame(Variable = c(paste("F( ", attention_abs_df1, ",", attention_abs_df2,")"),"R^2","p-value"),
                               Value = c(attention_abs_fstat,attention_abs_rsquared, attention_abs_pval))

kable(attention_abs_data, caption = "Executive Absolute AI Model Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r attention_abs_coefficients, echo = FALSE}
tab_model(mdl_attention_abs_AI, dv.labels = "Attention - Absolute AI",
          pred.labels = c("Intercept","Task Accuracy","DLPFC Absolute AI", "Hippocampus Absolute AI", "Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Executive_Attention Domain**
<div style="margin-bottom:100px;">
``` {r executive_attention_abs_data, echo = FALSE}
executive_attention_abs_data <- data.frame(Variable = c(paste("F( ", executive_attention_abs_df1, ",", executive_attention_abs_df2,")"),"R^2","p-value"),
                               Value = c(executive_attention_abs_fstat,executive_attention_abs_rsquared, executive_attention_abs_pval))

kable(executive_attention_abs_data, caption = "Executive_Attention Absolute AI Model Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r executive_attention_abs_coefficients, echo = FALSE}
tab_model(mdl_executive_attention_abs_AI, dv.labels = "Executive_Attention - Absolute AI",
          pred.labels = c("Intercept","Task Accuracy","DLPFC Absolute AI", "Hippocampus Absolute AI", "Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>


# FWHM Regressions

**New Model**

<div style="margin-bottom:100px;">
``` {r new_model_data, echo = FALSE}
new_model_data <- data.frame(Variable = c(paste("F( ", new_model_df1, ",", new_model_df2,")"),"R^2","p-value"),
                               Value = c(new_model_fstat,new_model_rsquared, new_model_pval))

kable(new_model_data, caption = "New Model Name Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r executive_attention_abs_coefficients, echo = FALSE}
tab_model(new_model, dv.labels = "New Model Title",
          pred.labels = c("Intercept","Task Accuracy","DLPFC Absolute AI", "Hippocampus Absolute AI", "Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>





