---
title: "KLU_APC2_Jinghang_Mountz_Data_Presentation"
author: "Li Jinghang, Ellie Mountz"
date: "7/23/2020"
output: "html_document"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# ```{r source, include=FALSE}
# source('/Users/elizabethmountz/Desktop/GitHub/KLU_APC2_Jinghang_Mountz_7_22_2020/R Script/KLU_APC2_Data_Analysis_7_22_2020.R')
# ```

``` {r dataCollect, include = FALSE, echo = FALSE}
rm(list=ls())
dev.off()
pacman::p_load(pacman, rio)
library(tibble)

# IMPORTING Data ###########################################################

data <- import("~/Desktop/GitHub/KLU_APC2_Jinghang_Mountz_7_22_2020/Appending_to_Master/KLU_APC2_Master_2020_07_22.xlsx")
activation <- import("~/Desktop/GitHub/KLU_APC2_Jinghang_Mountz_7_22_2020/Appending_to_Master/activ_values.txt")
AI <- import("~/Desktop/GitHub/KLU_APC2_Jinghang_Mountz_7_22_2020/Appending_to_Master/AI.txt")
FWHM <- import("~/Desktop/GitHub/KLU_APC2_Jinghang_Mountz_7_22_2020/Appending_to_Master/FWHM.txt")
FWHM <- abs(FWHM)

# data <- import("/Users/jinghangli/Documents/GitHub/KLU_APC2_Jinghang_Mountz_7_22_2020/KLU_APC2_Master_2020_07_22.xlsx")
# activation <- import("/Users/jinghangli/Documents/GitHub/KLU_APC2_Jinghang_Mountz_7_22_2020/Appending_to_Master/activ_values.txt")
# AI <- import("/Users/jinghangli/Documents/GitHub/KLU_APC2_Jinghang_Mountz_7_22_2020/Appending_to_Master/AI.txt")
# FWHM <- import("/Users/jinghangli/Documents/GitHub/KLU_APC2_Jinghang_Mountz_7_22_2020/Appending_to_Master/FWHM.txt")
# FWHM <- abs(FWHM)
# Filter Data ##############################################################
data <- data[-c(which(data$FaceNames_Exclude == 'Yes')),]
data <- data[data$Visit_Relative == 1,] #Issues with face name data and only 1 scan/subject - 87 observations
list <- match(activation$Scan_ID,data$Vault_Scan_ID)
index <- which(list!=0,arr.ind = T)
list <- na.omit(match(activation$Scan_ID, data$Vault_Scan_ID))

#creating new variables that are going to be appended
data$Subject_ID <- NA
data$Scan_ID <- NA
data$Left_Hippocampus_Activation <- NA
data$Right_Hippocampus_Activation <- NA
data$Left_DLPFC_Activation <- NA
data$Right_DLPFC_Activation <- NA
data$Hippocampus_AI <- NA
data$DLPFC_AI <-NA
data$Left_Hippocampus_FWHM <- NA
data$Right_Hippocampus_FWHM <- NA
data$Left_DLPFC_FWHM <- NA
data$Right_DLPFC_FWHM <- NA

#appending
data$Subject_ID[list] <- activation$Subject_ID[index]
data$Scan_ID[list] <- activation$Scan_ID[index]
data$Left_Hippocampus_Activation[list] <- activation[,3][index]
data$Right_Hippocampus_Activation[list] <- activation[,4][index]
data$Left_DLPFC_Activation[list] <- activation[,5][index]
data$Right_DLPFC_Activation[list] <- activation[,6][index]
data$Hippocampus_AI[list] <- AI[,3][index]
data$DLPFC_AI[list] <- AI[,4][index]

data$Left_Hippocampus_FWHM[list] <- FWHM[,3][index]
data$Right_Hippocampus_FWHM[list] <- FWHM[,4][index]
data$Left_DLPFC_FWHM[list] <- FWHM[,5][index]
data$Right_DLPFC_FWHM[list] <- FWHM[,6][index]

# Recode Variables ##############################################################
data$Race[data$Race == "NaN"] = NA
data$Race_cat <- data$Race != 'White' #non-white = TRUE
data$Education_cat <- data$Education > 12  #higher education = True
data$Sex[data$Sex == "NaN"] = NA
data$Sex_cat <- (data$Sex == 'Male') #TRUE = male
data$PiBStatus_SUVR_GTM_FS_Global[data$PiBStatus_SUVR_GTM_FS_Global == "NaN"] = NA
data$PiB_STATUS_CODE <- (data$PiBStatus_SUVR_GTM_FS_Global == "pos") #positive = TRUE
data$APOE_CODE[data$APOE_CODE == "NaN"] = NA
data$APOE_STATUS_CODE <- data$APOE_CODE == "At Least One E4 Allele" #E4 allele = TRUE
data$FaceName_PostScanAccuracy[data$FaceName_PostScanAccuracy == "NA"] <- NA
data$FaceName_PostScanAccuracy <- as.numeric(data$FaceName_PostScanAccuracy)
data$Abs_Hippocampus_AI <- abs(data$Hippocampus_AI)
data$Abs_DLPFC_AI <- abs(data$DLPFC_AI)
data$LETTER_FLUENCY <- (data$FLUENA + data$FLUENF+ data$FLUENS) / 3
data$WREC_TOT <- (data$WREC + data$WREC2 + data$WREC3)
Pred_STRCW <- (data$STRCOL*data$STRWRD) / (data$STRCOL+data$STRWRD)
data$STRINTERFERENCE <- data$STRCW - Pred_STRCW

#identifying PiB(+) subjects
x_l_h <- data$Left_Hippocampus_Activation[data$PiB_STATUS_CODE == TRUE]
y_l_h <- data$Left_Hippocampus_FWHM[data$PiB_STATUS_CODE == TRUE]
x_r_h <- data$Right_Hippocampus_Activation[data$PiB_STATUS_CODE == TRUE]
y_r_h <- data$Right_Hippocampus_FWHM[data$PiB_STATUS_CODE == TRUE]

x_l_d <-data$Left_DLPFC_Activation[data$PiB_STATUS_CODE == TRUE]
y_l_d <- data$Left_DLPFC_FWHM[data$PiB_STATUS_CODE == TRUE]
x_r_d <-data$Right_DLPFC_Activation[data$PiB_STATUS_CODE == TRUE]
y_r_d <- data$Right_DLPFC_FWHM[data$PiB_STATUS_CODE == TRUE]
#visulize data#################################################################
plot(data$Left_Hippocampus_Activation, data$Left_Hippocampus_FWHM,col="red", pch = 1, xlab="Mean Activation", ylab="FWHM")
points(data$Right_Hippocampus_Activation, data$Right_Hippocampus_FWHM, pch = 2, col="black")
points(x_l_h,y_l_h,pch = 4, cex = 2)
points(x_r_h,y_r_h,pch = 4, cex = 2)
legend(x=-2.5,y=27,c("Left Hippocampus", "Right Hippocampus", "PiB(+) Subjects"),cex=.8,col=c("red","black","black"),pch=c(1,2,4))

plot(data$Left_DLPFC_Activation, data$Left_DLPFC_FWHM,col="blue", pch = 1, xlab="Mean Activation", ylab="FWHM")
points(data$Right_DLPFC_Activation, data$Right_DLPFC_FWHM, col = "brown", pch =2)
points(x_l_d,y_l_d,pch = 4, cex = 2)
points(x_r_d,y_r_d,pch = 4, cex = 2)
legend(x=-4,y=35,c("Left DLPFC", "Right DLPFC","PiB(+) Subjects"),cex=.8,col=c("blue","brown","black"),pch=c(1,2,4))

# Cognitive Domain - Z Transform ####################################################################
#Negative z value means that lower value = higher performance
# doi:10.1016/j.jalz.2017.12.003 - method of composite calculation
#doi/ 10.1136/jnnp.2004.045567 - standard deviations from normative data
CLOCKD_Z <- (data$CLOCKD - mean(data$CLOCKD, na.rm = TRUE)) / sd(data$CLOCKD, na.rm = TRUE)
BLOCKDES_Z <- (data$BLOCKDES - mean(data$BLOCKDES, na.rm = TRUE)) / sd(data$BLOCKDES, na.rm = TRUE)
BNT60TOT_Z <- (data$BNT60TOT - mean(data$BNT60TOT, na.rm = TRUE)) / sd(data$BLOCKDE, na.rm = TRUE)
REYCO_Z <- (data$REYCO - mean(data$REYCO, na.rm = TRUE)) / sd (data$REYCO, na.rm = TRUE)
REYIM_Z <- (data$REYIM-mean(data$REYIM, na.rm = TRUE)) / sd(data$REYIM, na.rm = TRUE)
REYDE_Z <- (data$REYDE - mean(data$REYDE, na.rm = TRUE)) / sd(data$REYDE, na.rm = TRUE)
FLUEN_Z <- (data$FLUEN - mean(data$FLUEN, na.rm = TRUE)) / sd(data$FLUEN, na.rm = TRUE)
LETTER_FLUENCY_Z <- (data$LETTER_FLUENCY - mean(data$LETTER_FLUENCY, na.rm = TRUE)) / sd(data$LETTER_FLUENCY, na.rm=TRUE)
WREC_TOT_Z <- (data$WREC_TOT - mean(data$WREC_TOT, na.rm = TRUE)) / sd(data$WREC_TOT, na.rm =TRUE)
WRECDE_Z <- (data$WRECDE - mean(data$WRECDE, na.rm = TRUE)) / sd(data$WRECDE, na.rm = TRUE)
SPANSF_Z <- (data$SPANSF - mean(data$SPANSF, na.rm = TRUE)) / sd(data$SPANSF, na.rm = TRUE)
SPANSB_Z <- (data$SPANSB - mean(data$SPANSB, na.rm = TRUE)) / sd(data$SPANSB, na.rm = TRUE)
TRAILAS_Z <- (data$TRAILAS - mean(data$TRAILAS, na.rm = TRUE)) / sd(data$TRAILAS, na.rm = TRUE)
TRAILBS_Z <- (data$TRAILBS - mean(data$TRAILBS, na.rm = TRUE)) / sd(data$TRAILBS, na.rm= TRUE)
LMIAIMM_Z <- (data$LMIAIMM - mean(data$LMIAIMM, na.rm = TRUE)) /sd(data$LMIAIMM, na.rm = TRUE)
LMIIADEL_Z <- (data$LMIIADEL - mean(data$LMIIADEL, na.rm = TRUE))/sd(data$LMIIADEL, na.rm = TRUE)
DIGSYMWR_Z <- (data$DIGSYMWR - mean(data$DIGSYMWR, na.rm = TRUE))/sd(data$DIGSYMWR, na.rm = TRUE)
STRINTERFERENCE_Z <- (data$STRINTERFERENCE - mean(data$STRINTERFERENCE, na.rm = TRUE))/ sd(data$STRINTERFERENCE, na.rm = TRUE)
TRAILAS_Z_INV <- -1 * TRAILAS_Z
TRAILBS_Z_INV <- -1 * TRAILBS_Z

# Domain Scores #########################################################################
#doi:10.1016/j.jalz.2017.12.003., doi:10.1080/13607860903071014. (Both Beth Snitz articles), https://www.ncbi.nlm.nih.gov/books/NBK285344/ - for SPANSB in Executive
data$memory_learning <- (LMIAIMM_Z + REYIM_Z + WREC_TOT_Z) / 3
data$memory_retrieval <- (LMIIADEL_Z + REYDE_Z + WRECDE_Z) / 3
data$visuospatial <- (BLOCKDES_Z + REYCO_Z) / 2
data$language <- (FLUEN_Z + LETTER_FLUENCY_Z + BNT60TOT_Z) / 3
data$executive_attention <- (TRAILAS_Z_INV + TRAILBS_Z_INV + CLOCKD_Z + DIGSYMWR_Z + STRINTERFERENCE_Z + SPANSF_Z + SPANSB_Z) / 7
```

``` {r intraclass_correlation, include = FALSE, echo = FALSE}
#Intraclass Correlation ################################################################
# Pearson (Linear Correlation between composite and raw scores)
library("irr")
#Memory_Learning
REYIM_Pearson_Correlation <- cor(data$memory_learning, data$REYIM, use = "complete.obs")
LMIAIMM_Pearson_Correlation <- cor(data$memory_learning, data$LMIAIMM, use = "complete.obs")
WREC_TOT_Pearson_Correlation <- cor(data$memory_learning, data$WREC_TOT, use = "complete.obs")

#Memory_Retrieval
LMIIADEL_Pearson_Correlation <- cor(data$memory_learning, data$LMIIADEL, use = "complete.obs")
REYDE_Pearson_Correlation <- cor(data$memory_learning, data$REYDE, use = "complete.obs")
WRECDE_Pearson_Correlation <- cor(data$memory_learning, data$WRECDE, use = "complete.obs")

# Visuospatial
BLOCKDES_Pearson_Correlation <- cor(data$visuospatial, data$BLOCKDES, use = "complete.obs")
REYCO_Pearson_Correlation <- cor(data$visuospatial, data$REYCO, use = "complete.obs")

#Langugae
BNT60TOT_Pearson_Correlation <- cor(data$language, data$BNT60TOT, use = "complete.obs")
FLUEN_Pearson_Correlation <- cor(data$language, data$FLUEN, use = "complete.obs")
LETTER_FLUENCY_Pearson_Correlation <- cor(data$language, data$LETTER_FLUENCY, use = "complete.obs")

#Executive_Attention
TRAILBS_Combo_Pearson_Correlation <- cor(data$executive_attention, -1*data$TRAILBS, use = "complete.obs")
TRAILAS_Combo_Pearson_Correlation <- cor(data$executive_attention, -1*data$TRAILAS, use = "complete.obs")
SPANSF_Combo_Pearson_Correlation <- cor(data$executive_attention, data$SPANSF, use = "complete.obs")
DIGSYMWR_Combo_Pearson_Correlation <- cor(data$executive_attention, data$DIGSYMWR, use = "complete.obs")
SPANSB_Combo_Pearson_Correlation <- cor(data$executive_attention, data$SPANSB, use = "complete.obs")
CLOCKD_combo_Pearson_Correlation <- cor(data$executive_attention, data$CLOCKD, use = "complete.obs")

```

``` {r pval_calc, echo = FALSE, include = FALSE}
#For p-values
lmp <- function (modelobject) {
  if (class(modelobject) != "lm") stop("Not an object of class 'lm' ")
  f <- summary(modelobject)$fstatistic
  p <- pf(f[1],f[2],f[3],lower.tail=F)
  attributes(p) <- NULL
  return(p)
}
```

``` {r Abs_hippocampus, echo = FALSE}
mdl_Abs_hippocampus_AI <- lm(Abs_Hippocampus_AI ~ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_STATUS_CODE, data = data)

abs_hippocampus_rsquared <- summary(mdl_Abs_hippocampus_AI)$r.squared
abs_hippocampus_fstat <- summary(mdl_Abs_hippocampus_AI)$fstatistic[1]
abs_hippocampus_df1 <- summary(mdl_Abs_hippocampus_AI)$fstatistic[2]
abs_hippocampus_df2 <- summary(mdl_Abs_hippocampus_AI)$fstatistic[3]
abs_hippocampus_pval <- lmp(mdl_Abs_hippocampus_AI)
```

``` {r Abs_DLPFC, echo = FALSE}
mdl_Abs_DLPFC_AI <- lm(Abs_DLPFC_AI ~ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_STATUS_CODE, data = data)

abs_DLPFC_rsquared <- summary(mdl_Abs_DLPFC_AI)$r.squared
abs_DLPFC_fstat <- summary(mdl_Abs_DLPFC_AI)$fstatistic[1]
abs_DLPFC_df1 <- summary(mdl_Abs_DLPFC_AI)$fstatistic[2]
abs_DLPFC_df2 <- summary(mdl_Abs_DLPFC_AI)$fstatistic[3]
abs_DLPFC_pval <- lmp(mdl_Abs_DLPFC_AI)

```

``` {r memory_learning_abs, echo = FALSE}
# Cognitive Factors  - Absolute AI################################################################
mdl_memory_learning_abs_AI <- lm(memory_learning ~ FaceName_PostScanAccuracy+Abs_DLPFC_AI + Abs_Hippocampus_AI+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_STATUS_CODE, data = data)

memory_learning_abs_rsquared <- summary(mdl_memory_learning_abs_AI)$r.squared
memory_learning_abs_fstat <- summary(mdl_memory_learning_abs_AI)$fstatistic[1]
memory_learning_abs_df1 <- summary(mdl_memory_learning_abs_AI)$fstatistic[2]
memory_learning_abs_df2 <- summary(mdl_memory_learning_abs_AI)$fstatistic[3]
memory_learning_abs_pval <- lmp(mdl_memory_learning_abs_AI)

```

``` {r memory_retrieval_abs, echo = FALSE}
mdl_memory_retrieval_abs_AI <- lm(memory_retrieval ~ FaceName_PostScanAccuracy+Abs_DLPFC_AI + Abs_Hippocampus_AI+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_STATUS_CODE, data = data)

memory_retrieval_abs_rsquared <- summary(mdl_memory_retrieval_abs_AI)$r.squared
memory_retrieval_abs_fstat <- summary(mdl_memory_retrieval_abs_AI)$fstatistic[1]
memory_retrieval_abs_df1 <- summary(mdl_memory_retrieval_abs_AI)$fstatistic[2]
memory_retrieval_abs_df2 <- summary(mdl_memory_retrieval_abs_AI)$fstatistic[3]
memory_retrieval_abs_pval <- lmp(mdl_memory_retrieval_abs_AI)

```

``` {r visuospatial_abs, echo = FALSE}

mdl_visuospatial_abs_AI <- lm(visuospatial ~ FaceName_PostScanAccuracy+Abs_DLPFC_AI + Abs_Hippocampus_AI+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_STATUS_CODE, data = data)

visuospatial_abs_rsquared <- summary(mdl_visuospatial_abs_AI)$r.squared
visuospatial_abs_fstat <- summary(mdl_visuospatial_abs_AI)$fstatistic[1]
visuospatial_abs_df1 <- summary(mdl_visuospatial_abs_AI)$fstatistic[2]
visuospatial_abs_df2 <- summary(mdl_visuospatial_abs_AI)$fstatistic[3]
visuospatial_abs_pval <- lmp(mdl_visuospatial_abs_AI)

```

``` {r language_abs, echo = FALSE}

mdl_language_abs_AI <- lm(language ~ FaceName_PostScanAccuracy+Abs_DLPFC_AI + Abs_Hippocampus_AI+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_STATUS_CODE, data = data)

language_abs_rsquared <- summary(mdl_language_abs_AI)$r.squared
language_abs_fstat <- summary(mdl_language_abs_AI)$fstatistic[1]
language_abs_df1 <- summary(mdl_language_abs_AI)$fstatistic[2]
language_abs_df2 <- summary(mdl_language_abs_AI)$fstatistic[3]
language_abs_pval <- lmp(mdl_language_abs_AI)

```

``` {r executive_attention_abs, echo = FALSE}
mdl_executive_attention_abs_AI <- lm(executive_attention ~ FaceName_PostScanAccuracy+Abs_DLPFC_AI + Abs_Hippocampus_AI+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_STATUS_CODE, data = data)

executive_attention_abs_rsquared <- summary(mdl_executive_attention_abs_AI)$r.squared
executive_attention_abs_fstat <- summary(mdl_executive_attention_abs_AI)$fstatistic[1]
executive_attention_abs_df1 <- summary(mdl_executive_attention_abs_AI)$fstatistic[2]
executive_attention_abs_df2 <- summary(mdl_executive_attention_abs_AI)$fstatistic[3]
executive_attention_abs_pval <- lmp(mdl_executive_attention_abs_AI)
```

``` {r fwhm_L_hippocampus, echo = FALSE}
# Regression Models FWHM #####################################################################################
mdl_left_hippocampus_fwhm <- lm(Left_Hippocampus_FWHM ~ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_STATUS_CODE, data = data)

left_hippocampus_rsquared <- summary(mdl_left_hippocampus_fwhm)$r.squared
left_hippocampus_fstat <- summary(mdl_left_hippocampus_fwhm)$fstatistic[1]
left_hippocampus_df1 <- summary(mdl_left_hippocampus_fwhm)$fstatistic[2]
left_hippocampus_df2 <- summary(mdl_left_hippocampus_fwhm)$fstatistic[3]
left_hippocampus_pval <- lmp(mdl_left_hippocampus_fwhm)
```

``` {r fwhm_R_hippocampus, echo = FALSE}
mdl_right_hippocampus_fwhm <- lm(Right_Hippocampus_FWHM ~ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_STATUS_CODE, data = data)

right_hippocampus_rsquared <- summary(mdl_right_hippocampus_fwhm)$r.squared
right_hippocampus_fstat <- summary(mdl_right_hippocampus_fwhm)$fstatistic[1]
right_hippocampus_df1 <- summary(mdl_right_hippocampus_fwhm)$fstatistic[2]
right_hippocampus_df2 <- summary(mdl_right_hippocampus_fwhm)$fstatistic[3]
right_hippocampus_pval <- lmp(mdl_right_hippocampus_fwhm)
```

``` {r fwhm_L_dlpfc, echo = FALSE}
mdl_left_dlpfc_fwhm <- lm(Left_DLPFC_FWHM ~ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_STATUS_CODE, data = data)

left_dlpfc_rsquared <- summary(mdl_left_dlpfc_fwhm)$r.squared
left_dlpfc_fstat <- summary(mdl_left_dlpfc_fwhm)$fstatistic[1]
left_dlpfc_df1 <- summary(mdl_left_dlpfc_fwhm)$fstatistic[2]
left_dlpfc_df2 <- summary(mdl_left_dlpfc_fwhm)$fstatistic[3]
left_dlpfc_pval <- lmp(mdl_left_dlpfc_fwhm)
```

``` {r fwhm_R_dlpfc, echo = FALSE}
mdl_right_dlpfc_fwhm <- lm(Right_DLPFC_FWHM ~ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_STATUS_CODE, data = data)

right_dlpfc_rsquared <- summary(mdl_right_dlpfc_fwhm)$r.squared
right_dlpfc_fstat <- summary(mdl_right_dlpfc_fwhm)$fstatistic[1]
right_dlpfc_df1 <- summary(mdl_right_dlpfc_fwhm)$fstatistic[2]
right_dlpfc_df2 <- summary(mdl_right_dlpfc_fwhm)$fstatistic[3]
right_dlpfc_pval <- lmp(mdl_right_dlpfc_fwhm)
```

``` {r memory_learning_fwhm, echo = FALSE}
# Cognitive Factors  - FWHM ################################################################
mdl_memory_learning_fwhm <- lm(memory_learning ~ FaceName_PostScanAccuracy + Left_Hippocampus_FWHM + Right_Hippocampus_FWHM +Left_DLPFC_FWHM + Right_DLPFC_FWHM+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_STATUS_CODE, data = data)

memory_learning_fwhm_rsquared <- summary(mdl_memory_learning_fwhm)$r.squared
memory_learning_fwhm_fstat <- summary(mdl_memory_learning_fwhm)$fstatistic[1]
memory_learning_fwhm_df1 <- summary(mdl_memory_learning_fwhm)$fstatistic[2]
memory_learning_fwhm_df2 <- summary(mdl_memory_learning_fwhm)$fstatistic[3]
memory_learning_fwhm_pval <- lmp(mdl_memory_learning_fwhm)
```

``` {r memory_retrieval_fwhm, echo = FALSE}
mdl_memory_retrieval_fwhm <- lm(memory_retrieval ~ FaceName_PostScanAccuracy + Left_Hippocampus_FWHM + Right_Hippocampus_FWHM +Left_DLPFC_FWHM + Right_DLPFC_FWHM+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_STATUS_CODE, data = data)

memory_retrieval_fwhm_rsquared <- summary(mdl_memory_retrieval_fwhm)$r.squared
memory_retrieval_fwhm_fstat <- summary(mdl_memory_retrieval_fwhm)$fstatistic[1]
memory_retrieval_fwhm_df1 <- summary(mdl_memory_retrieval_fwhm)$fstatistic[2]
memory_retrieval_fwhm_df2 <- summary(mdl_memory_retrieval_fwhm)$fstatistic[3]
memory_retrieval_fwhm_pval <- lmp(mdl_memory_retrieval_fwhm)
```

``` {r visuospatial_fwhm, echo = FALSE}

mdl_visuospatial_fwhm <- lm(visuospatial ~ FaceName_PostScanAccuracy + Left_Hippocampus_FWHM + Right_Hippocampus_FWHM +Left_DLPFC_FWHM + Right_DLPFC_FWHM+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_STATUS_CODE, data = data)

visuospatial_fwhm_rsquared <- summary(mdl_visuospatial_fwhm)$r.squared
visuospatial_fwhm_fstat <- summary(mdl_visuospatial_fwhm)$fstatistic[1]
visuospatial_fwhm_df1 <- summary(mdl_visuospatial_fwhm)$fstatistic[2]
visuospatial_fwhm_df2 <- summary(mdl_visuospatial_fwhm)$fstatistic[3]
visuospatial_fwhm_pval <- lmp(mdl_visuospatial_fwhm)
```

``` {r language_fwhm, echo = FALSE}

mdl_language_fwhm <- lm(language ~FaceName_PostScanAccuracy + Left_Hippocampus_FWHM + Right_Hippocampus_FWHM +Left_DLPFC_FWHM + Right_DLPFC_FWHM+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_STATUS_CODE, data = data)

language_fwhm_rsquared <- summary(mdl_language_fwhm)$r.squared
language_fwhm_fstat <- summary(mdl_language_fwhm)$fstatistic[1]
language_fwhm_df1 <- summary(mdl_language_fwhm)$fstatistic[2]
language_fwhm_df2 <- summary(mdl_language_fwhm)$fstatistic[3]
language_fwhm_pval <- lmp(mdl_language_fwhm)
```

``` {r executive_attention_fwhm, echo = FALSE}

mdl_executive_attention_fwhm <- lm(executive_attention ~ FaceName_PostScanAccuracy+ Left_Hippocampus_FWHM + Right_Hippocampus_FWHM +Left_DLPFC_FWHM + Right_DLPFC_FWHM+ Age_CurrentVisit+Sex_cat+Race_cat+Education_cat+FDG_SUVR_GTM_FS_Global+PiB_STATUS_CODE+APOE_STATUS_CODE, data = data)

executive_attention_fwhm_rsquared <- summary(mdl_executive_attention_fwhm)$r.squared
executive_attention_fwhm_fstat <- summary(mdl_executive_attention_fwhm)$fstatistic[1]
executive_attention_fwhm_df1 <- summary(mdl_executive_attention_fwhm)$fstatistic[2]
executive_attention_fwhm_df2 <- summary(mdl_executive_attention_fwhm)$fstatistic[3]
executive_attention_fwhm_pval <- lmp(mdl_executive_attention_fwhm)
```

``` {r modelSetUp, echo = FALSE, include = FALSE}
if (!require("sjPlot")) install.packages("sjPlot")
library(sjPlot)
if (!require("kableExtra")) install.packages("kableExtra")
library(knitr)
library(kableExtra)
if (!require("scales")) install.packages("scales")
library(scales)
```
## Regression Models:

## Hemispheric Asymmetry Models

**Hippocampus Absolute Asymmetry Index Data**
<div style="margin-bottom:100px;">
``` {r abs_hippocampus_data, echo = FALSE}
abs_hippocampus_data <- data.frame(Variable = c(paste("F( ", abs_hippocampus_df1, ",", abs_hippocampus_df2,")"),"R^2","p-value"),
                               Value = c(abs_hippocampus_fstat,abs_hippocampus_rsquared,abs_hippocampus_pval))

kable(abs_hippocampus_data, caption = "Hippocampus Absolute AI Model Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

``` {r abs_hippocampus_coefficients, echo = FALSE}
tab_model(mdl_Abs_hippocampus_AI, dv.labels = "Hippocampus Absolute AI",
          pred.labels = c("Intercept","Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**DLPFC Absolute Asymmetry Index Data** 
<div style="margin-bottom:100px;">
``` {r abs_DLPFC_data, echo = FALSE}
abs_DLPFC_data <- data.frame(Variable = c(paste("F( ", abs_DLPFC_df1, ",", abs_DLPFC_df2,")"),"R^2","p-value"),
                               Value = c(abs_DLPFC_fstat,abs_DLPFC_rsquared,abs_DLPFC_pval))

kable(abs_DLPFC_data, caption = "DLPFC Absolute AI Model Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r abs_DLPFC_coefficients, echo = FALSE}
tab_model(mdl_Abs_DLPFC_AI, dv.labels = "DLPFC Absolute AI",
          pred.labels = c("Intercept","Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

## Cogntive Domains (Abs AI)

**Memory Learning Domain**
<div style="margin-bottom:100px;">
``` {r memory_learning_abs_data, echo = FALSE}
memory_learning_abs_data <- data.frame(Variable = c(paste("F( ", memory_learning_abs_df1, ",", memory_learning_abs_df2,")"),"R^2","p-value"),
                               Value = c(memory_learning_abs_fstat,memory_learning_abs_rsquared,memory_learning_abs_pval))

kable(memory_learning_abs_data, caption = "Memory Learning Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r memory_learning_abs_coefficients, echo = FALSE}
tab_model(mdl_memory_learning_abs_AI, dv.labels = "Memory Learning",
          pred.labels = c("Intercept","Task Accuracy","DLPFC Absolute AI", "Hippocampus Absolute AI", "Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Memory Retrieval Learning Domain**
<div style="margin-bottom:100px;">
``` {r memory_abs_data, echo = FALSE}
memory_retrieval_abs_data <- data.frame(Variable = c(paste("F( ", memory_retrieval_abs_df1, ",", memory_retrieval_abs_df2,")"),"R^2","p-value"),
                               Value = c(memory_retrieval_abs_fstat,memory_retrieval_abs_rsquared,memory_retrieval_abs_pval))

kable(memory_retrieval_abs_data, caption = "Memory Retrieval Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r memory_abs_coefficients, echo = FALSE}
tab_model(mdl_memory_retrieval_abs_AI, dv.labels = "Memory Retrieval",
          pred.labels = c("Intercept","Task Accuracy","DLPFC Absolute AI", "Hippocampus Absolute AI", "Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Visuospatial Domain**
<div style="margin-bottom:100px;">
``` {r visuospatial_abs_data, echo = FALSE}
visuospatial_abs_data <- data.frame(Variable = c(paste("F( ", visuospatial_abs_df1, ",", visuospatial_abs_df2,")"),"R^2","p-value"),
                               Value = c(visuospatial_abs_fstat,visuospatial_abs_rsquared,visuospatial_abs_pval))

kable(visuospatial_abs_data, caption = "Visuospatial Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r visuospatial_abs_coefficients, echo = FALSE}
tab_model(mdl_visuospatial_abs_AI, dv.labels = "Visuospatial",
          pred.labels = c("Intercept","Task Accuracy","DLPFC Absolute AI", "Hippocampus Absolute AI", "Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Language Domain**
<div style="margin-bottom:100px;">
``` {r language_abs_data, echo = FALSE}
language_abs_data <- data.frame(Variable = c(paste("F( ", language_abs_df1, ",", language_abs_df2,")"),"R^2","p-value"),
                               Value = c(language_abs_fstat,language_abs_rsquared, language_abs_pval))

kable(language_abs_data, caption = "Language Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r language_abs_coefficients, echo = FALSE}
tab_model(mdl_language_abs_AI, dv.labels = "Language",
          pred.labels = c("Intercept","Task Accuracy","DLPFC Absolute AI", "Hippocampus Absolute AI", "Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Executive_Attention Domain**
<div style="margin-bottom:100px;">
``` {r executive_attention_abs_data, echo = FALSE}
executive_attention_abs_data <- data.frame(Variable = c(paste("F( ", executive_attention_abs_df1, ",", executive_attention_abs_df2,")"),"R^2","p-value"),
                               Value = c(executive_attention_abs_fstat,executive_attention_abs_rsquared, executive_attention_abs_pval))

kable(executive_attention_abs_data, caption = "Executive_Attention Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r executive_attention_abs_coefficients, echo = FALSE}
tab_model(mdl_executive_attention_abs_AI, dv.labels = "Executive_Attention",
          pred.labels = c("Intercept","Task Accuracy","DLPFC Absolute AI", "Hippocampus Absolute AI", "Age at Visit", "Sex", "Race",
                          "Education (years)", "FDG Global", 
                          "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>


# FWHM Regressions

**Left Hippocampus FWHM**
<div style="margin-bottom:100px;">
``` {r left_hippocampus_fwhm_data, echo = FALSE}
left_hippocampus_fwhm_data <- data.frame(Variable = c(paste("F( ", left_hippocampus_df1, ",", left_hippocampus_df2,")"),"R^2","p-value"),
                               Value = c(left_hippocampus_fstat,left_hippocampus_rsquared, left_hippocampus_pval))

kable(left_hippocampus_fwhm_data, caption = "Left Hippocampus FWHM Summary", digits = 3) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r left_hippocampus_fwhm_coefficients, echo = FALSE}
tab_model(mdl_left_hippocampus_fwhm, dv.labels = "Left Hippocampus FWHM",
          pred.labels = c("Intercept","Age","Sex", "Race", "Education (years)", "FDG Global", "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Right Hippocampus FWHM**
<div style="margin-bottom:100px;">
``` {r right_hippocampus_fwhm_data, echo = FALSE}
right_hippocampus_fwhm_data <- data.frame(Variable = c(paste("F( ", right_hippocampus_df1, ",", right_hippocampus_df2,")"),"R^2","p-value"),
                               Value = c(right_hippocampus_fstat,right_hippocampus_rsquared, right_hippocampus_pval))

kable(right_hippocampus_fwhm_data, caption = "Right Hippocampus FWHM Summary", digits = 3) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r right_hippocampus_fwhm_coefficients, echo = FALSE}
tab_model(mdl_right_hippocampus_fwhm, dv.labels = "Right Hippocampus FWHM",
          pred.labels = c("Intercept","Age","Sex", "Race", "Education (years)", "FDG Global", "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Left DLPFC FWHM**
<div style="margin-bottom:100px;">
``` {r left_dlpfc_fwhm_data, echo = FALSE}
left_dlpfc_fwhm_data <- data.frame(Variable = c(paste("F( ", left_dlpfc_df1, ",", left_dlpfc_df2,")"),"R^2","p-value"),
                               Value = c(left_dlpfc_fstat,left_dlpfc_rsquared, left_dlpfc_pval))

kable(left_dlpfc_fwhm_data, caption = "Left DLPFC FWHM Summary", digits = 3) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r left_dlpfc_fwhm_coefficients, echo = FALSE}
tab_model(mdl_left_dlpfc_fwhm, dv.labels = "Left DLPFC FWHM",
          pred.labels = c("Intercept","Age","Sex", "Race", "Education (years)", "FDG Global", "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Right DLPFC FWHM**
<div style="margin-bottom:100px;">
``` {r right_dlpfc_fwhm_data, echo = FALSE}
right_dlpfc_fwhm_data <- data.frame(Variable = c(paste("F( ", right_dlpfc_df1, ",", right_dlpfc_df2,")"),"R^2","p-value"),
                               Value = c(right_dlpfc_fstat,right_dlpfc_rsquared, right_dlpfc_pval))

kable(right_dlpfc_fwhm_data, caption = "Right DLPFC FWHM Summary", digits = 3) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r right_dlpfc_fwhm_coefficients, echo = FALSE}
tab_model(mdl_right_dlpfc_fwhm, dv.labels = "Right DLPFC FWHM",
          pred.labels = c("Intercept","Age","Sex", "Race", "Education (years)", "FDG Global", "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

## Cogntive Domains (FWHM)
**Memory Learning Domain**
<div style="margin-bottom:100px;">
``` {r memory_learning_fwhm_data, echo = FALSE}
memory_learning_fwhm_data <- data.frame(Variable = c(paste("F( ", memory_learning_fwhm_df1, ",", memory_learning_fwhm_df2,")"),"R^2","p-value"),
                               Value = c(memory_learning_fwhm_fstat,memory_learning_fwhm_rsquared,memory_learning_fwhm_pval))

kable(memory_learning_fwhm_data, caption = "Memory Learning Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r memory_learning_fwhm_coefficients, echo = FALSE}
tab_model(mdl_memory_learning_fwhm, dv.labels = "Memory Learning",
          pred.labels = c("Intercept","FaceName_PostScanAccuracy", "Left_Hippocampus_FWHM","Right_Hippocampus_FWHM", "Left_DLPFC_FWHM", "Right_DLPFC_FWHM", "Age at Visit", "Sex",  "Race","Education (years)", "FDG Global", "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Memory Retrieval Learning Domain**
<div style="margin-bottom:100px;">
``` {r memory_retrieval_fwhm_data, echo = FALSE}
memory_retrieval_fwhm_data <- data.frame(Variable = c(paste("F( ", memory_retrieval_fwhm_df1, ",", memory_retrieval_fwhm_df2,")"),"R^2","p-value"),
                               Value = c(memory_retrieval_fwhm_fstat,memory_retrieval_fwhm_rsquared,memory_retrieval_fwhm_pval))

kable(memory_retrieval_fwhm_data, caption = "Memory Retrieval Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r memory_retrieval_fwhm_coefficients, echo = FALSE}
tab_model(mdl_memory_retrieval_fwhm, dv.labels = "Memory Retrieval",
          pred.labels = c("Intercept","FaceName_PostScanAccuracy", "Left_Hippocampus_FWHM","Right_Hippocampus_FWHM", "Left_DLPFC_FWHM", "Right_DLPFC_FWHM", "Age at Visit", "Sex",  "Race","Education (years)", "FDG Global", "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Visuospatial Domain**
<div style="margin-bottom:100px;">
``` {r visuospatial_fwhm_data, echo = FALSE}
visuospatial_fwhm_data <- data.frame(Variable = c(paste("F( ", visuospatial_fwhm_df1, ",", visuospatial_fwhm_df2,")"),"R^2","p-value"),
                               Value = c(visuospatial_fwhm_fstat, visuospatial_fwhm_rsquared, visuospatial_fwhm_pval))

kable(visuospatial_fwhm_data, caption = "Visuospatial Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r visuospatial_fwhm_coefficients, echo = FALSE}
tab_model(mdl_visuospatial_fwhm, dv.labels = "Visuospatial",
          pred.labels = c("Intercept","FaceName_PostScanAccuracy", "Left_Hippocampus_FWHM","Right_Hippocampus_FWHM", "Left_DLPFC_FWHM", "Right_DLPFC_FWHM", "Age at Visit", "Sex",  "Race","Education (years)", "FDG Global", "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Language Domain**
<div style="margin-bottom:100px;">
``` {r language_fwhm_data, echo = FALSE}
language_fwhm_data <- data.frame(Variable = c(paste("F( ", language_fwhm_df1, ",", language_fwhm_df2,")"),"R^2","p-value"),
                               Value = c(language_fwhm_fstat, language_fwhm_rsquared, language_fwhm_pval))

kable(language_fwhm_data, caption = "Language Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r language_fwhm_coefficients, echo = FALSE}
tab_model(mdl_language_fwhm, dv.labels = "Language",
          pred.labels = c("Intercept","FaceName_PostScanAccuracy", "Left_Hippocampus_FWHM","Right_Hippocampus_FWHM", "Left_DLPFC_FWHM", "Right_DLPFC_FWHM", "Age at Visit", "Sex",  "Race","Education (years)", "FDG Global", "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>

**Executive_Attention Domain**
<div style="margin-bottom:100px;">
``` {r Executive_Attention_fwhm_data, echo = FALSE}
executive_attention_fwhm_data <- data.frame(Variable = c(paste("F( ", executive_attention_fwhm_df1, ",", executive_attention_fwhm_df2,")"),"R^2","p-value"),
                               Value = c(executive_attention_fwhm_fstat, executive_attention_fwhm_rsquared, executive_attention_fwhm_pval))

kable(executive_attention_fwhm_data, caption = "Executive_Attention Summary", digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

``` {r executive_attention_fwhm_coefficients, echo = FALSE}
tab_model(mdl_executive_attention_fwhm, dv.labels = "Executive_Attention",
          pred.labels = c("Intercept", "FaceName_PostScanAccuracy", "Left_Hippocampus_FWHM","Right_Hippocampus_FWHM", "Left_DLPFC_FWHM", "Right_DLPFC_FWHM", "Age at Visit", "Sex",  "Race","Education (years)", "FDG Global", "PiB Global Status", "APOE Status"), show.r2 = FALSE, show.ci = FALSE)
```
</div>




